---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# codexplor
­ЪД░­ЪћД­Ъће UNDER CONSTRUNCTION ­ЪД░­ЪћД­Ъће
<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/codexplor)](https://CRAN.R-project.org/package=codexplor)
<!-- badges: end -->

The goal of codexplor is to Explore Your Codes Files, with a bunch of dedicated func'. Soon, you should try to :

РЈЕ Get a network of funcРђЎ iby passing a folder path to get_text_network_from_files()

РЈЕ Get metrics and identifying cascading dependancies of func' [­ЪћД­Ъће]

РЈЕ Identifying your higher-level func' and visualize the ones they launch [­ЪћД­Ъће]

РЈЕ Made some cool dataviz' about your func' network [­ЪћД­Ъће]

And other features, more or less useful for coordinate large programming project, made helper func' for new colleagues and/or future you, and chill in front of cool megalomaniac dataviz about your programming world.

## Installation

You can't install the development version of codexplor yet

``` r
cat("...")
```

## Example

A - not so - lovely dog <3 is waiting here :

```{r example}
library(codexplor)
## basic example code
dog <- c("
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРбђРБђРБђРБаРБцРБцРБцРБцРБцРБцРБёРБђРАђРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ░РАЙРаЏРаЅРаЅРаЅРаЂРађРађРађРађРаЅРаЅРаЅРаЏРаиРБдРБђРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ░РАЈРађРађРађРађРађРађРађРађРађРађРађРађРБђРАђРађРаѕРаЎРб┐РБёРБђРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ┐РАЄРађРађРађРађРађРађРађРађРађРађРбаРАЙРаЏРаЏРбиРАєРађРађРаЅРаЅРаЏРаХРБдРБёРађРађРађРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРбИРАЄРађРађРађРађРађРађРађРађРађРБаРА┐РаЃРађРађРађРађРађРађРађРађРађРађРађРаЎРб┐РБдРАђРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРаѕРАЄРађРађРађРађРађРађРађРбђРБ┤РаЪРаЂРађРађРађРађРађРађРађРађРађРађРађРађРађРађРаЎРб┐РБєРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРб░РАЄРађРађРађРађРађРБаРБ┤РаЪРБЁРБаРБђРАђРађРађРађРађРађРађРађРађРађРађРађРађРађРађРаѕРб╗РБДРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ╝РаЄРађРађРбђРБаРБЙРаЪРаЂРбИРБ┐РБ┐РА┐Рб┐РАєРађРађРађРађРађРбђРБцРађРађРађРађРађРађРађРађРб┐РБєРАђРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ░РаЪРађРбђРБ┤РаЪРБ┐РаЃРађРађРаИРБ┐РБ┐РБиРАЙРаЃРађРађРбђРБаРБХРАЪРаЂРађРађРађРађРађРађРађРађРађРа┐РБдРАёРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ┤РаЈРБаРАЙРаЏРаЂРБИРАЄРађРађРађРађРаѕРаЅРаЅРбђРБаРА┤РаџРаІРБАРАЪРађРађРађРађРађРађРађРађРбаРБёРађРађРаўРБ┐РАђРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРбаРБЙРА┐РаЏРаІРађРађРбђРА┐РађРађРБђРБаРБцРаќРаЏРаЏРаЅРаЂРађРађРађРА┐РађРађРађРађРађРађРађРађРађРађРб╗РађРађРађРаИРБиРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРаЎРаЅРађРађРађРађРбђРБЙРбЂРБ┤РаЪРаІРаЅРађРађРађРађРађРађРађРађРБИРаЄРађРБаРБХРБХРБдРАђРађРађРађРбђРБ┐РађРађРађРађРб╗РБДРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБаРБЙРБ┐РаІРађРађРађРбђРАђРађРађРађРађРађРађРб░РаЈРађРађРБ┐РБ┐РБ┐РаЪРАЄРађРађРађРБ╝РАЈРађРађРађРађРађРб┐РАєРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРбаРБЙРаІРбИРБДРађРађРађРаИРб┐РБ┐РБ┐РБдРАђРађРађРађРАЪРађРађРађРаЎРа┐Ра┐РаџРаЂРађРбђРБ╝РаЈРађРађРађРађРађРађРаИРБ┐Рађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ░РАЪРаЂРађРаўРБ┐РБцРБђРађРаѕРБ┐РБ┐Рб┐РБ┐РАЄРађРађРађРАЄРађРађРађРађРађРађРађРБаРБ┤РБ┐РаІРађРађРађРађРађРађРађРбаРБ┐РаЂ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ╝РаЈРађРађРађРађРб╣РАЇРаЏРбиРБёРаЅРаЅРаЂРаЅРађРађРађРБ╝РаЃРађРађРађРБђРБцРБХРа┐Рб╗РБ┐РаЂРађРађРађРађРађРбђРБаРБ┤РаЪРаЂРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ░РАЈРађРађРађРађРађРађРа╗РБєРАђРб╗РБєРађРађРађРађРбђРБ╝РБЂРБђРБцРАХРа┐РаЏРБ┐РАцРађРБ╝РаЄРађРађРађРбђРБцРАХРаЪРаІРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРађРБ┐РаЂРађРађРађРађРађРађРађРаѕРаЅРаЏРаЏРа╗РаХРаХРаЙРаЪРаЏРаЅРаЅРаЂРађРађРађРаЏРБиРађРБ┐РађРађРађРБ┤РАЪРаІРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРБИРА┐РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРаѕРб┐РАЄРБ┐РађРађРБ╝РАЈРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРађРБ┐РАЄРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРбИРБиРб╣РБЄРбаРА┐РађРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРађРБ╝РБ┐РАЄРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРбИРБ┐РаѕРб┐РБЙРаЄРађРађРађРађРађРађРађРађРађРађ
РађРађРађРађРађРађРађРађРађРађРађРБЙРаЈРаИРБ┐РађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРађРбИРБ┐РађРаИРа┐РађРађРађРађРађРађРађРађРађРађРађ
")
```


I don't need to render `README.Rmd` regularly, since keep `README.md` up-to-date is near to useless. `devtools::build_readme()` is handy for this.

I can also embed plots but it's cool to forget to replace the default url :

```{r pressure, echo = FALSE}
plot(pressure)

# In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

```

