---
title: "Turn a programming project into a corpus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Turn a programming project into a corpus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(codexplor)

```

**`codexplor::construct_corpus`** turn a programming project into a text-mining corpus, given :

- folder(s) path(s) and/or github repo(s) of the project ;
- and programming language(s) - default is `'R'`.

**Supported languages.** By default `construct_corpus` will analyze .R files, but one or several `languages` could be indicated. Recognized languages are `r paste0(names(get_def_regex_by_language()) , collapse = ", ")`. 

## Examples


```{r example, result = 'asis',eval = T}
library(codexplor)

# 1) Construct a corpus without a Citations network
  corp <- construct_corpus( repos =  "clement-LVD/codexplor", languages = "R")
  
  str(corp, max.level = 1) 
  
```

     # Example : several local folders and repos
    corpus <- construct_corpus(c("~", "M:/") languages = "R"
    , repos =  c("clement-LVD/codexplor","tidyverse/stringr"))
   
    # Example : several languages
    corpus_py <- construct_corpus(repos = "secdev/scapy"
    , languages = c("Python", "Javascript"), .verbose = T) #take a while


## Understand the corpus.list
**List of dataframes.** `construct_corpus` return a `corpus.list` object, a standard `list` of 4 dataframes : 

- `codes` (classes `corpus.lines` & `data.frame`)
- `comments` (classes `corpus.lines` & `data.frame`)
- `files` (classes `corpus.nodelist` & `data.frame`)
- `functions` (classes `corpus.nodelist` & `data.frame`)

Further complementary analyzes will add others dataframes to the list, e.g., a network of internal dependencies (classes `citations.network`, `internal.dependencies` & `data.frame`).


**Details.** 

- The `files` `data.frame` is sorted by files, and contains the files path and/or url, and overall text-mining metrics about each files of the corpus (e.g., number of characters, words count).

- The `functions` `data.frame` contains the functions names and text-mining metrics about these functions.

- The 2 `corpus.lines` `data.frame` are related to lines (file path and content of each lines, line number, and text-mining metrics related to each lines). 

The `codes` `data.frame` (one of the `corpus.lines` dataframes) have more columns, such as :

- a `commented` column (inline comment at the end of a codeline)
<!-- - and a `matches` column that contain internally-exposed functions names, e.g., if a `pol  <- function` is defined within a file, the 1st `matches` corresponding entry for this line will be `'pol'`. -->

Further complementary analyzes will add others columns, e.g., as soon as a network of `internal.dependencies` is computed, some metrics are added to the `files` data.frame of the `corpus.list`.

## Default patterns
`construct_corpus` rely on some default patterns, designed to analyze a programming project in a standardized way. 
With these patterns, `construct_corpus` will :

1. read the files accordingly to their extension, e.g., R language is associated with `'.R'` files. 
2. process commented lines accordingly to each language definition, e.g., R & Python use `'#'` and don't allow multi-lines comments, contrary to JavaScript.
3. isolate the exposed content, i.e. not quoted and not within a `'{ }'`.
4. extract functions names from the exposed content, in order to list the internally exposed functions of the programming project.

```{r table-operations-construct-corpus, eval=FALSE, include=FALSE}

steps <- data.frame(Step = c("Filter files path/url and read only files with correct extension(s)"  
, "**Separate commented lines** from *codes lines*"  
, "**Identify the unested - exposed - content** within the *codes lines*, in order to exclude the non-exposed functions (*aka* nested functions) from the matches of the next step"
 , "**Extract functions names** within the *codes lines* (1st matches)"
)
 , Examples = c(paste('e.g., "R" language is associated with "`.R`" files and a default filtering pattern (i.e."'
                      , get_def_regex_by_language()$R$pattern_to_exclude, '")'  )
, 'e.g., R & Python files have commented lines that begin with "`#`", others languages commented lines begin with "`//`". Commented blocks on several lines use ("`/*`")'
, "e.g., extract exposed content - within the project - that is not under a block of code delimitor such as '{' and '}' for the R language"
  , 'e.g., the name is before a "`<- function(`" instruction for the R programming language'
)

)

rownames(steps) <- c("1. Read", "2. Preprocess" ,"3. Identify", "4. Qualify")

colnames(steps) <- c("Steps", "Examples of pattern associated with language(s)")

knitr::kable(steps,row.names = T )

```

The hereafter table show some examples of a `hello` function defined in several languages : `construct_corpus` have to match `'hello'`, despite of the differences between languages.

```{r table-langages-differences, echo=FALSE}
require(codexplor)
listee <- get_def_regex_by_language(return_examples = T)
# from our function in raw-data
tablee <- do.call(rbind.data.frame,  listee) 

table <- tablee[,!colnames(tablee) %in% c("regex_func_name" , "fn_regex", "local_file_ext", "nested_codes")]

colnames(table) <- gsub(x=colnames(table), "_|delim_pair_", " ")

table <- table[order(rownames(table)), ]  

knitr::kable(table)

```

Here, R is the only language that assign an anonymous function to an object. Thus, contrary to other languages, we have to find the name of R functions before the keyword 'function', R parameters names are within the parenthesis after 'function(', etc. 

## Unmatched func' def'
The function 'hello' defined as a lambda (anonymous) function within the Python line hereafter is not matched yet by `construct_corpus` :

     hello = lambda: None

Another caveat unsupported - yet - is the 'hello' javascript function defined hereafter :

     const hello = (a, b) => a + b;
     
The re-assigning of an anonymous R function to a new R object is not supported yet :
      
      aaa <- function(i, a){i + a} # construct_corpus match the 'aaa' function
       my_func_a <- aaa    #  but don't notice the creation of an alias
      my_func_a(1,2) # will not be matched during the post-processing 

### Helper functions that rely on `construct_corpus`
`codexplor::get_doc_network_from_project` is an helper 'high-level' function that perform an analysis of the internal dependencies by performing a 2nd matches from the 1st matches of `construct_corpus`, e.g., see the [vignette about analyzing a network of internal dependencies with `get_doc_network_from_project`](https://clement-lvd.github.io/codexplor/articles/vignette_citations.network_df_of_internal.dependencies.html).
