---
title: "Turn a programming project into a corpus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Turn a programming project into a corpus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
require(codexplor)
```

# Constructing your corpus
`codexplor` offer a standardized protocol to turn a programming project into a text-mining corpus, by providing to `construct_corpus` language(s) to analyze, folder(s) path(s) and/or github repo(s).

    corpus <- construct_corpus("~", "tidyverse/stringr", languages = "R")

    # Return a standard `list` of `df` (a `corpus.list` object).

This function will compute some text-mining metrics within each line and within document-level (e.g., number of characters, words count).

### About default patterns associated with each language
Standardized patterns are used along the way of constructing a corpus. For each of the `languages` supported by `construct_corpus` :

```{r table-operations-construct-corpus, echo=FALSE}

steps <- data.frame(Step = c("Read the files of the local folder(s) and/or github public repo(s) accordingly to their extension"  
, "Separate commented lines from code lines"                    
 , "Extract a 1st matched-text within the codes lines, accordingly to a pattern"

)
 , Examples = c('e.g., "R" language is associated with "`.R`" files and with a filtering pattern (e.g., files with "`test-`", "`vignettes`", "`Rcheck`" in their full names are excluded)'   
, 'e.g., R & Python files generally have each commented lines that begin with "`#`", others languages should have commented blocks separeted on several lines (e.g., `/* [comments] */`'
  , 'e.g.,  default pattern is catching the names of the functions defined within a file, e.g., for the R programming language : the name is before a "`<- function(`" instruction'
)

)

colnames(steps) <- c("Steps", "Examples of pattern associated with language(s)")

knitr::kable(steps,row.names = T )

```

By default `construct_corpus` try to analyze .R files. One or several `languages` could be passed to `construct_corpus`. Planned languages are : `r paste0(names(get_def_regex_by_language()), collapse = ", ")`

### About duplicated lines associated with 1st matches
`construct_corpus` perform a 1st text-extraction, accordingly to a pattern. During this 1st matches extraction, lines are duplicated *when several matches are found on the same line*. 

> For example, by default, the names of functions defined in the files of the project are extracted during the 1st match operated by `construct_corpus`. If a file have several function defined *within the same line*, such a line will be duplicated in the returned `df`, with several 'matches' entries along these lines and an identical line_number. 
