---
title: "Citations Network computed by codexplor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Citations Network computed by codexplor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This Vignette give a basic understanding of the `citations.network` `dataframe` : a Citations Network of functions within programming project(s) computed by some of the `codexplor` reporting protocols, i.e. `codexplor::get_doc_network_from_project()` and other functions that rely on `compute_doc_network_from_corpus`. 

This particular `citations.network` `dataframe` is one of the cornerstones of `codexplor`, in order to made 'clusters' of files before further processing, e.g., before to aggregate readability statistics to this 'cluster' level.

### Network properties
The returned `citations.network` `dataframe` is the edgelist^[Edgelist is the one of the standard representation of a graph (https://igraph.org/r/doc/as_edgelist.html).] of a document-to-document citations network. These networks have basic properties, not covered here (e.g., a citations network is a directed network).

Regarding the `citations.network` `dataframe` of the `corpus.list` `list` of dataframes :

- Nodes are the programming files, default is a network of .R files. 
- Edges go from the file that calls a function to the file where the function is defined.

> `codexplor` default pattern are aimed to extract functions names from the files of a *programming* project (see next section). 

Thus, in a typical programming project :

- Nodes are files, so mostly - or only - functions ;
- Â°â† Indegree of a file is "how many files are calling the function(s) defined in this file" ;
- Â°â†’ Outdegree of a file is "how many functions are used by this file" ; 
- âŸ² Auto-mentioning refear to 'recursivity' (`codexplor` default is to filter autolinks).

### Cascading matching operated by `compute_doc_network_from_corpus`
Given a `corpus.list` created with `construct_corpus`, `codexplor::compute_doc_network_from_corpus()` will try to perform a 'cascading matching' :

â© Transform the *1st matches* added by `codexplor::construct_corpus` into a pattern. The default are supposed to extract *R functions names as a 1st matches*, e.g., we have defined 'Pier', 'Pol' and 'Jak' - functions - names in 3 separates files. 

â© And search for these patterns in the initial content , in order to constitute a Citations Network with these 2nd matches, e.g., a programming file is citing 'Pier', 'Pol' and 'Jak' and thus this file is linked to the files where we previously found the 1st matches.

ðŸŽ Return the edgelist that symbolize this network of *documents*. Default is a network of internal dependencies within the files of a programming project : links are beginning from the programming file that is calling a function => to the programming file where this function is defined.

### Function call that are non-supported during 2nd matches
Some way of writing a program are not fully supported, such as :

**Python instantiated methods.** The instantiated Python methods are not supported yet by `get_doc_network_from_project`, i.e. `obj.method()`.

If we take this Python code sample, the 1st match is realized by `construct_corpus`, but `get_doc_network_from_project` don't perform a 2nd match.

```{r eval = F }
#  Consider the Python code herafter 
class A:
    def method(self):
        return "My custom method"
 # construct_corpus return 'method' as a 1stly matched function name

obj = A()
obj.method() # Return : 'My custom method'

# get_doc_network_from_project don't identify the 2nd match because of the prefix ("obj.")
```


### Filter undesired match
Junk nodes needs to be excluded from the network. Typical "false positive" matches are the lines where you use the name of another function in a message, e.g. `message("my_func() is deprecated. You should use this_function() instead)`. `get_doc_network_from_project` offer several parameters for dealing with your style of writing a program.


