---
title: "Citations Network of Internal Dependencies computed by codexplor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Citations Network of Internal Dependencies computed by codexplor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This Vignette explain the `data.frame` with additional classes `citations.network` and `internal.dependencies`. This type of `data.frame` is the edgelist of a Citations Network of functions or files within programming project(s).  

## Network properties

### Overall Considerations : about the `citations.network` `data.frame` 
`codexplor::construct_corpus` protocols add a `citations.network` class of `data.frame` to the main `corpus.list`. 

This `citations.network` `data.frame` is an edgelist^[Edgelist is the one of the standard representation of a graph (https://igraph.org/r/doc/as_edgelist.html).] that symbolize the programming project as a document-to-document citations network : a network of documents, citing each others. 

`codexplor` offers several levels-of-depth, e.g., the nodes of a `citations.network` `data.frame` could be the functions or the programming files of the corpus.

> A citations network have theoretical network properties, not covered here (e.g., a citations network is a directed network). 

### Networks of `internal.dependencies`
Some `data.frame` of the `corpus.list` have additional classes `citations.network` and `internal.dependencies` : the `files.network` and `functions.network` df. In these networks :

```{r echo=FALSE}
nett <- t(data.frame(Name= c("`files.network`", "`functions.network`" )
,  Nodes = c("Programming files", "Functions")
, Links = c("Start from a programming file that calls a function and point to the programming file where the function is defined", "start from a function that call another function and point to this 2nd function")
, Indegrees = c("°← How many files of the project(s) are calling the function(s) defined in this file", "°← How many functions of the project(s) are calling this function" )
, Outdegrees = c("°→ Number of files of the project(s) where the functions used by this file are defined", "°→ How many functions of the project(s) are used by this function")
, Automentioning = c("(`codexplor` default is to filter out autolinks within files)" ,"Recursivity")
) )



knitr::kable(nett)
```

> See a dataviz' of a `files.network` in the short [example of documents network](https://clement-lvd.github.io/codexplor/articles/vignette_analyse_citations_network_from_project.html)

## Technical details

**Cascading matching.** Given a `corpus.list` created with `construct_corpus` a cascading matching :

1. `codexplor::construct_corpus` extract exposed functions names from files where these functions are defined, e.g., have found 'Pier', 'pol' and 'jak' function names in 3 separate files.
2. The functions that calls these functions are identified, e.g., a function is calling `'Pier('`, `'pol('` and `'jak('` and the function is linked to these 3 functions.
3. Similarly, a network of files is constructed, e.g., the code of a programming file is calling `'Pier('`, `'pol('` and `'jak('` and this file is linked to the files where these functions are defined.

**Match functions names.** `construct_corpus` rely on some default patterns, designed to analyze a programming project in a standardized way. 
Accordingly to these patterns, `construct_corpus` will :

1. read the files accordingly to their extension, e.g., R language is associated with `'.R'` files. 
2. process commented lines accordingly to each language definition, e.g., R & Python use `'#'` and don't allow multi-lines comments, contrary to JavaScript.
3. isolate the exposed content, i.e. not quoted and not within a `'{ }'`.
4. extract functions names from the exposed content, in order to list the internally exposed functions of the programming project.

**Examples.** The hereafter table show some examples of a `hello` function defined in several languages : `construct_corpus` have to match `'hello'`, despite of the differences between languages.

```{r table-langages-differences, echo=FALSE, message=FALSE, warning=FALSE}
require(codexplor)
listee <- get_def_regex_by_language(return_examples = T)
# from our function in raw-data
tablee <- do.call(rbind.data.frame,  listee) 

table <- tablee[,!colnames(tablee) %in% c("regex_func_name" , "fn_regex", "local_file_ext", "nested_codes")]

colnames(table) <- gsub(x=colnames(table), "_|delim_pair_", " ")

table <- table[order(rownames(table)), ]  

knitr::kable(table)

```

Here, R is the only language that assign an anonymous function to an object. Thus, contrary to other languages, we have to find the name of R functions before the keyword 'function', R parameters names are within the parenthesis after 'function(', etc. 

## Unmatched definition
**Python.** The function 'hello' defined as a lambda (anonymous) function within the Python line hereafter is not matched yet by `construct_corpus` :

     hello = lambda: None

**R.** The re-assigning of an anonymous R function to a new R object is not supported yet :
      
      aaa <- function(i, a){i + a} # construct_corpus match the 'aaa' function
       my_func_a <- aaa    #  but don't notice the creation of an alias
      my_func_a(1,2) # will not be matched during the post-processing 

<!-- **JS.** Another caveat unsupported - yet - is the 'hello' javascript function defined hereafter : -->

<!--      const hello = (a, b) => a + b; -->

## Function call that are non-supported during 2nd matches
Some way of writing a program are not fully supported during the 2nd matches.

**Python instantiated methods.** If we take this Python code sample hereafter, the 1st match is realized by `construct_corpus`, but `codexplor` can't match the instantiated Python methods, i.e. `obj.method()`.

```{r eval = F }
#  Consider the Python code herafter 
class A:
    def method(self):
        return "My custom method"
 # construct_corpus return 'method' as a 1stly matched function name

obj = A()
obj.method() # Return : 'My custom method'

# construct_corpus don't identify the 2nd match because of the prefix ("obj.")
```


## Filter undesired match
Junk nodes needs to be excluded from the returned networks, such as the lines where you use the name of another function in a message, e.g. `message("my_func() is deprecated. You should use this_function() instead)`. 

`construct_corpus` offer the `exclude_quoted_content` parameter, in order to exclude quoted text from the matches and avoid this false positive case.

      construct_corpus("~", languages = "R", exclude_quoted_content = TRUE) 
      
Be aware that all the quoted text will be avoided, if you've included some - fancy - way of *call* a function as a quoted `character` chain.


