---
title: "Turn a programming project into a corpus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Turn a programming project into a corpus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

# Constructing your corpus
`codexplor::construct_corpus` offer a standardized protocol to turn a programming project into a text-mining corpus, given :

- folder(s) path(s) and/or github repo(s) to analyze ;
- and programming language(s) - default is `'R'`.


```{r example, result = 'asis',eval = T}
library(codexplor)

# 1) Construct a corpus without a Citations network
  corp <- construct_corpus( repos =  "clement-LVD/codexplor", languages = "R")
  
  str(corp, max.level = 1) 
  
```

     # More examples :
    corpus <- construct_corpus( languages = "R"
    , repos =  "clement-LVD/codexplor","tidyverse/stringr"))
    
    corpus_py <- construct_corpus(repos = "secdev/scapy"
    , languages = "Python", .verbose = T) #take a while

**Supported languages.** By default `construct_corpus` try to read and analyze .R files. One or several `languages` could be indicated. Recognized languages are `r paste0(names(get_def_regex_by_language()) , collapse = ", ")`. 

### Returned list of data.frame
**corpus.list of dataframes.** `construct_corpus` return a `corpus.list` object, a standard `list` of 3 dataframes, i.e. 2 `corpus.lines` and 1 `corpus.nodelist` dataframes. 

Complementary or specific analyzes will add others dataframes to the list, e.g., a network of internal dependancies (classes `citations.network` & `dataframe`).

**Text-mining metrics.** 
Each lines and each documents are associated with text-mining metrics (e.g., number of characters, words count). Within the returned `list` of dataframes, these metrics are relative to : 

- a specific line for the `corpus.lines` dataframes
- or to the entire document for the `corpus.nodelist` `dataframe` .

The `codes` `dataframe` (one of the `corpus.lines` dataframes) have a '`matches`' column, a specialized way of understand a line. These 1st matches are explained hereafter.

### About the 1st matches operated
**1st matches operated.** Given language(s), `construct_corpus` try to perform an initial identification within the content. 

> By default, these 1st matches are supposed to be the function names, for functions defined within a file.

Thus, `construct_corpus` rely on some default patterns, associated with the supported languages. 


### Default patterns associated with languages
For each of the required language(s), a default standardized patterns is used for :

```{r table-operations-construct-corpus, echo=FALSE}

steps <- data.frame(Step = c("Filter files path/url accordingly to some patterns and read only the selected programming files with the correct extension(s)"  
, "Separate commented lines from *codes lines*"                    
 , "Perform 1st matches within the *codes lines* (default try to extract the functions names)"
, "Refine and post-process the *codes lines*"
)
 , Examples = c('e.g., "R" language is associated with "`.R`" files and a filtering pattern (e.g., files with "`test-`", "`vignettes`", "`Rcheck`" in their full names are excluded)'   
, 'e.g., R & Python files generally have each commented lines that begin with "`#`", others languages should have commented blocks separeted on several lines (e.g., `/* [comments] */`'
  , 'e.g.,  default patterns are crafted for extract the names of the functions defined within a file, e.g., for the R programming language : the name is before a "`<- function(`" instruction'
, "e.g., specifical delimitors of a block of code such as '{' and '}' within a .R file are used to determine if a given 1st match - function definition - is included within another function definition as an inner function (*aka* nested function)"
)

)

colnames(steps) <- c("Steps", "Examples of pattern associated with language(s)")

knitr::kable(steps,row.names = T )

```

> These default patterns are crafted specifically to analyze a programming project in a standardized way, given a programming language.

### About duplicated lines associated with 1st matches
`construct_corpus` perform a 1st text-extraction, accordingly to a pattern. During this 1st matches extraction, lines are duplicated *when several matches are found on the same line*. 

> For example, by default, the names of functions defined in the files of the project are extracted during the 1st match operated by `construct_corpus`. If a file have several function defined *within the same line*, such a line will be duplicated in the returned `df`, with several 'matches' entries along these lines and an identical line_number. 

### Helper functions that rely on `construct_corpus`

`codexplor::get_doc_network_from_project` is an helper 'high-level' function that perform an analysis of the internal dependancies by constructing a corpus and perform a 2nd matches and network analyses, e.g., see the [vignette of `get_doc_network_from_project`](https://clement-lvd.github.io/codexplor/articles/vignette_get_doc_network_from_project.html).
